A Domain Specific Language for SpectreGuard

### 2020-12-06 paper/main.tex
Included other Int literal typing rule
Some examples in paper

\begin{figure}[h]
  \centering
\resizebox{0.68\linewidth}{!}{
\begin{minipage}{\linewidth}
  \centering
\begin{gather*}
  \inference{}{\ttt{Public :: Sensitivity}}\\
\\
  \inference{}{\ttt{Secret :: Sensitivity}}\\
\\
  \inference{n \in \mathbb{N}}{\ttt{$n$ :: Expr $\sigma$ Int}}\\
\\
  \inference{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ Int}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ Int}}
    {\Gamma \vdash \ttt{x + y :: Expr $\sigma$ Int}}\\
  \\
  \inference{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ Int}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ Int}}
    {\Gamma \vdash \ttt{x <? y :: Expr $\sigma$ Bool}}\\
  \\
  \inference{%
    \Gamma \vdash \ttt{a :: Expr $\sigma$ (Ptr $\tau$)}
    & \Gamma \vdash \ttt{i :: Expr $\sigma$ Int}}
    {\Gamma \vdash \ttt{a ! i :: Expr $\sigma$ $\tau$}}\\
  \\
  \inference{\Gamma \vdash \ttt{n :: Int}}{\Gamma \vdash \ttt{allocPublic @$\tau$ n :: Cmd (Expr Public (Ptr $\tau$))}}\\
\\
  \inference{\Gamma \vdash \ttt{n :: Int}}{\Gamma \vdash \ttt{allocSecret @$\tau$ n :: Cmd (Expr Secret (Ptr $\tau$))}}\\
\\
  \inference{\Gamma \vdash \ttt{x :: $\tau$}}{\Gamma \vdash \ttt{decl x :: Cmd (Expr Public $\tau$)}}\\
\\
  \inference{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ $\tau$}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ $\tau$}}
    {\Gamma \vdash \ttt{x .= y :: Cmd ()}}\\
  \\
  \inference{%
    \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
    &\Gamma \vdash \ttt{t :: $\tau$}
    &\Gamma \vdash \ttt{f :: $\tau$}}
    {\Gamma \vdash \ttt{ifThenElse cond t f :: Cmd ()}}\\
  \\
  \inference{%
    \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
    & \Gamma \vdash \ttt{body :: Cmd $\alpha$}}
    {\Gamma \vdash \ttt{while cond body :: Cmd ()}}\\
  \\
  \inference{%
    \Gamma \vdash \ttt{init :: Expr $\sigma$ $\tau$}\\
    \Gamma \vdash \ttt{fn :: Expr $\sigma$ $\tau$ $\rarr$ (Expr $\sigma$ Bool, Cmd (), Cmd ())}
    }{\Gamma \vdash \ttt{for init fn :: Cmd ()}}\\
  \\
  \inference{%
    \Gamma \vdash \ttt{c :: Cmd (Expr $\sigma$ $\tau$)}
    & \ttt{x} \notin dom(\Gamma)
    \\ \Gamma \vdash \ttt{($\lambda$ x $\rarr$ body) :: Expr $\sigma$ $\tau$ $\rarr$ Cmd $\alpha$}
  }{%
    \Gamma \vdash \ttt{(\textbf{do} \{ x <- c; body \}) :: Cmd $\alpha$}
  }
\end{gather*}
\end{minipage}}
  \caption{Typing rules for sensitivity types}
\label{fig:SensTypes}
\end{figure}

@@

\section{Information Flow Analysis}
\begin{figure}[h]
  \centering
\resizebox{0.68\linewidth}{!}{
\begin{minipage}{\linewidth}
  \centering
\begin{gather*}
  \inference{%
    \Delta;\Gamma \vdash \ttt{x :: $\tau$}
    \\ \Delta;\Gamma \vdash \ttt{k :: Expr Public $\tau$ $\rarr$ Cmd $\alpha$}
    \\ \Delta;\Gamma\vdash A(\ttt{decl v >>= ($\lambda$x $\rarr$ k)})
    }
    {%
      \Delta,Pub(x);\Gamma \vdash A(\ttt{k})
    }\\
    \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{x :: Expr Public $\tau$}
    & \Delta;\Gamma \vdash \ttt{y :: Expr Public $\tau$}
    \\ \Delta;\Gamma \vdash \ttt{k :: () $\rarr$ Cmd $\alpha$}
    & \Delta;\Gamma \vdash A(\ttt{(x .= y) >>= k})
    \\ \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
    }
    {%
      \Delta;\Gamma \vdash \ttt{x} \sarr L(\ttt{x})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    & \Delta;\Gamma \vdash \ttt{body :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{while cond body})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{body})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{t})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{f})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash v \in L(\ttt{x})
    }
    {%
      \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
    }
\end{gather*}
\end{minipage}}
  \caption{Information flow analysis rules which define the relation $\sarr$}
\label{fig:FlowRules}
\end{figure}
...
\section{Examples}
...
% \section{Your System}
% ...
% \section{Evaluation}
% ...

>>>>

\begin{figure}[h]
  \centering
\resizebox{0.68\linewidth}{!}{
\begin{minipage}{\linewidth}
  \centering
\begin{gather*}
  \inference{}{\ttt{Public :: Sensitivity}}\\
\\
  \inference{}{\ttt{Secret :: Sensitivity}}\\
\\
  \inference{n \in \mathbb{N}}{\ttt{$n$ :: Int}}\\
  \\
  \inference{n \in \mathbb{N}}{\ttt{$n$ :: Expr $\sigma$ Int}}\\
\\
  \inference{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ Int}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ Int}}
    {\Gamma \vdash \ttt{x + y :: Expr $\sigma$ Int}}\\
  \\
  \inference{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ Int}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ Int}}
    {\Gamma \vdash \ttt{x <? y :: Expr $\sigma$ Bool}}\\
  \\
  \inference{%
    \Gamma \vdash \ttt{a :: Expr $\sigma$ (Ptr $\tau$)}
    & \Gamma \vdash \ttt{i :: Expr $\sigma$ Int}}
    {\Gamma \vdash \ttt{a ! i :: Expr $\sigma$ $\tau$}}\\
  \\
  \inference{\Gamma \vdash \ttt{n :: Int}}{\Gamma \vdash \ttt{allocPublic @$\tau$ n :: Cmd (Expr Public (Ptr $\tau$))}}\\
\\
  \inference{\Gamma \vdash \ttt{n :: Int}}{\Gamma \vdash \ttt{allocSecret @$\tau$ n :: Cmd (Expr Secret (Ptr $\tau$))}}\\
\\
  \inference{\Gamma \vdash \ttt{x :: $\tau$}}{\Gamma \vdash \ttt{decl x :: Cmd (Expr Public $\tau$)}}\\
\\
  \inference{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ $\tau$}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ $\tau$}}
    {\Gamma \vdash \ttt{x .= y :: Cmd ()}}\\
  \\
  \inference{%
    \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
    &\Gamma \vdash \ttt{t :: $\tau$}
    &\Gamma \vdash \ttt{f :: $\tau$}}
    {\Gamma \vdash \ttt{ifThenElse cond t f :: Cmd ()}}\\
  \\
  \inference{%
    \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
    & \Gamma \vdash \ttt{body :: Cmd $\alpha$}}
    {\Gamma \vdash \ttt{while cond body :: Cmd ()}}\\
  \\
  \inference{%
    \Gamma \vdash \ttt{init :: Expr $\sigma$ $\tau$}\\
    \Gamma \vdash \ttt{fn :: Expr $\sigma$ $\tau$ $\rarr$ (Expr $\sigma$ Bool, Cmd (), Cmd ())}
    }{\Gamma \vdash \ttt{for init fn :: Cmd ()}}\\
  \\
  \inference{%
    \Gamma \vdash \ttt{c :: Cmd (Expr $\sigma$ $\tau$)}
    & \ttt{x} \notin dom(\Gamma)
    \\ \Gamma \vdash \ttt{($\lambda$ x $\rarr$ body) :: Expr $\sigma$ $\tau$ $\rarr$ Cmd $\alpha$}
  }{%
    \Gamma \vdash \ttt{(\textbf{do} \{ x <- c; body \}) :: Cmd $\alpha$}
  }
\end{gather*}
\end{minipage}}
  \caption{Typing rules for sensitivity types}
\label{fig:SensTypes}
\end{figure}

@@

\section{Examples}

A couple of simple examples illustrate the basic typing rules:

\begin{lstlisting}[language=haskell]
example1 :: Cmd ()
example1 = do
  array1 <- allocSecret @Int 8
  array2 <- allocSecret @Int 8

  array2 .= array1
\end{lstlisting}

\noindent This first example passes the type checker with no problem: the array copy
is being performed from one secret array to another secret array.

The next example does not type check:

\begin{lstlisting}[language=haskell]
  -- This example fails to type check
example2 :: Cmd ()
example2 = do
  array1 <- allocSecret @Int 8
  array2 <- allocPublic @Int 8
  (*@\color{red}array2 .= array1@*)
\end{lstlisting}

\noindent \ttt{example2} fails to type check since \ttt{array1} and \ttt{array2} have
different sensitivity annotations, while the type of the \ttt{(.=)} operation
requires that both arguments have the same sensitivity annotation. This restriction can
be seen in the typing rule for \ttt{(.=)} in Fig. \ref{fig:SensTypes}.

Turning to more complex examples, we can see that the following example type checks

\begin{lstlisting}
example3 :: Cmd ()
example3 = do
  arrayA <- allocSecret @Int 8
  arrayB <- allocSecret @Int 8

  for (0 :: Expr Secret Int) (\i -> ((i <? 8), (i += 1), do
    (arrayA ! i) .= (arrayB ! i)))
\end{lstlisting}

\noindent This demonstrates a basic \ttt{for} loop and the array indexing syntax. Again, the
only copies happen between two variables with the same sensitivity level, so this
program is well-typed.

The next slightly more complex example exhibits a limitation of this sensitivity type checking

\begin{lstlisting}
example4 :: Cmd ()
example4 = do
  secretArray <- allocSecret @Int 8
  publicArray <- allocPublic @Int 8

  for (0 :: Expr Public Int) (\i -> ((i <? 8), (i += 1), do
    leak <- decl (0 :: Int)
    for (0 :: Expr Secret Int) (\j -> ((j <? (secretArray ! i))
                                      ,(j += 1)
                                      ,do
      leak += 1))
    (publicArray ! i) .= leak))
\end{lstlisting}

In this code, the entire contents of the secret variable \ttt{secretArray} is leaked
to the public variable \ttt{publicArray}, despite the two variables having different
sensitivity annotations and therefore type checking without error. This is the
result of information being indirectly leaked from the secret variable to the
public variable via a control flow construct: in this case, the innermost \ttt{for} loop.

\section{Information Flow Analysis}
\begin{figure}[h]
  \centering
\resizebox{0.68\linewidth}{!}{
\begin{minipage}{\linewidth}
  \centering
\begin{gather*}
  \inference{%
    \Delta;\Gamma \vdash \ttt{x :: $\tau$}
    \\ \Delta;\Gamma \vdash \ttt{k :: Expr Public $\tau$ $\rarr$ Cmd $\alpha$}
    \\ \Delta;\Gamma\vdash A(\ttt{decl v >>= ($\lambda$x $\rarr$ k)})
    }
    {%
      \Delta,Pub(x);\Gamma \vdash A(\ttt{k})
    }\\
    \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{x :: Expr Public $\tau$}
    & \Delta;\Gamma \vdash \ttt{y :: Expr Public $\tau$}
    \\ \Delta;\Gamma \vdash \ttt{k :: () $\rarr$ Cmd $\alpha$}
    & \Delta;\Gamma \vdash A(\ttt{(x .= y) >>= k})
    \\ \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
    }
    {%
      \Delta;\Gamma \vdash \ttt{x} \sarr L(\ttt{x})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    & \Delta;\Gamma \vdash \ttt{body :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{while cond body})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{body})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{t})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{f})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash v \in L(\ttt{x})
    }
    {%
      \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
    }
\end{gather*}
\end{minipage}}
  \caption{Information flow analysis rules which define the relation $\sarr$}
\label{fig:FlowRules}
\end{figure}
...

% \section{Your System}
% ...
% \section{Evaluation}
% ...
